---
title: "echolocatoR Fine-mapping Portal" 
author: "<h4>Author: <i>Brian M. Schilder</i></h4>"
date: "<h4>Updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{echolocatoR_Finemapping_Portal} 
    %\usepackage[utf8]{inputenc}
    %\VignetteEngine{knitr::rmarkdown}  
---

```{r style, echo=FALSE, results='asis', message=FALSE}
BiocStyle::markdown()
knitr::opts_chunk$set(tidy = FALSE,
                      message = FALSE)
```

```{r setup}
library(echodata)
```

The *echolocatoR.

The following functions provides API access to the fine-mapping results, 
pre-computed LD matrices, and plots available on the [**echolocatoR Fine-mapping Portal**](https://rajlab.shinyapps.io/Fine_Mapping_Shiny/).

# View metadata

Peruse the metadata to see the available 
data types (e.g. "GWAS", "QTL"), 
datasets (e.g. "Ripke_2014", "Wray_2018"), and 
phenotypes (e.g. "Schizophrenia", "Major Depressive Disorder").

```{r}
meta <- echodata::portal_metadata()
knitr::kable(meta)
```

# Query portal

Query and download data from the [**echolocatoR Fine-mapping Portal**](https://rajlab.shinyapps.io/Fine_Mapping_Shiny/).

`portal_query` will return a list of paths where each file 
has been downloaded locally, in a hierarchical folder structure 
(i.e. `dataset_type --> dataset --> locus --> data_types` )

```{r}
results_dir <- tempdir()
local_files <- echodata::portal_query(dataset_types="GWAS",
                                      phenotypes = c("schizophrenia",
                                                     "parkinson"),
                                      file_types = c("multi_finemap","LD"),
                                      loci = c("BST1","CHRNB1","LRRK2"),
                                      LD_panels = "UKB",
                                      results_dir = results_dir)
knitr::kable(utils::head(local_files))
```

### Merge fine-mapping results  

Next, we can gather all of the fine-mapping results generated by
`finemap_loci()` previously.  
`merge_finemapping_results` recursively searches for the correct files
within a hierarchical folder structure and imports only the multi-finemap files. 

```{r merge_finemapping_results()} 
merged_DT <- echodata::merge_finemapping_results(dataset = results_dir,   
                                                 minimum_support = 0,
                                                 include_leadSNPs = TRUE,
                                                 consensus_thresh = 2)
echodata::results_report(merged_DT)
knitr::kable(utils::head(merged_DT))
```

## Import LD 

Next, we import the a subset of the LD matrices for only the lead SNP.

```{r}
ld_files <- local_files[file_type=="LD",]
ld_matrices <- lapply(stats::setNames(ld_files$path_local, 
                                      ld_files$locus),
                      function(x){
  data.table::fread(x)
}) 
knitr::kable(utils::head(ld_matrices[[1]]))
```

# Session Info 

<details> 

```{r Session Info}
utils::sessionInfo()
```

</details>  

